---
title: "Lab 07 - Modelling course evaluations"
author: [TEAM NAME]
output: 
  tufte::tufte_html:
    css: ../lab.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes

---

### Load packages 

```{r load-packages, message=FALSE}
library(tidyverse)
library(tidymodels)
library(patchwork)
```

### Read in data

```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


### Exercise 1

```{r viz-score}
ggplot(data = evals, mapping = aes(x = score))+
  geom_bar()
```

The distribution is skewed towards the higher ratings. It is expected because students do not want to be too critical of their professors and courses, and additionally they have usually chosen courses that interest them so they would be biased generally to prefer the courses they have chosen. 

### Exercise 2

```{r viz-score-bty, eval = FALSE}
# add the code for each plot and assign them to the names as outlined below
# remove eval = FALSE from the code chunk options
# knit the document, and you'll see them appear next to each other
# this uses the patchwork package loaded above
# learn more about patchwork at https://patchwork.data-imaginist.com/
# it might be useful for your presentations!
plot_geom_point  <- ggplot(___)

plot_geom_jitter <- ggplot(___)

plot_geom_point + plot_geom_jitter
```

*Add your narrative here.*

### Exercise 3

```{r fit-score_bty_fit}
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit}
tidy(score_bty_fit)
```

score = 3.880 + 0.067bty_avg 

### Exercise 4

```{r viz-score_bty_fit}
# add your code here
```

### Exercise 5

For each additional point in average beauty rating a professor has, their score increases by 0.067.

### Exercise 6

The intercept estimate of 3.88 makes sense as a professor with a beauty rating of 0 should be able to teach a course.

### Exercise 7

```{r glance-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)
```

The r.squared value of 0.035 indicates that there is a very weak correlation between a professor's average beauty and the score they get.

### Exercise 8

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___)
```

*Add your narrative here.*

### Exercise 9

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 10

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "___") %>%
  select(___) %>%
  pull()
```

*Add your narrative here.*

### Exercise 11

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 12

```{r glance-score_bty_gender_fit}
# glance model output
```

*Add your narrative here.*

### Exercise 13

*Add your linear model here. Don't worry about math notation, you can use things like score-hat.*

### Exercise 14

*Add your narrative here. One sentence is sufficient.*

### Exercise 15

*Add your narrative here. One sentence is sufficient.*

### Exercise 16

*Add your narrative here. One sentence is sufficient.*

### Exercise 17

*Add your narrative here. One sentence is sufficient.*

### Exercise 18

```{r fit-score_bty_gender_rank_fit}
# fit model

# glance model output
```

*Add your narrative here. One sentence is sufficient.*
